An Introduction to Return Oriented Programming

### 2023-02-16 paper.tex
changes

\section{Theory}
\subsection{Stack}
The following graphic is an illustration of how the stack changes when injecting the payload. The buffer first has to be filled. In binary exploitation the letter \Verb+A+ is used for that most of the time, it has an easy to identify hexadecimal value of \bltInlineVerb{0x41}. It is important to note that without any special compiler options the stack will be aligned in \bltInlineVerb{dword}'s, because of that the buffer has to be filled with 16 Bytes instead of 8 Bytes, this can be turned off with the option \bltInlineVerb{-mpreferred-stack-boundary=2}. Though, then the payload only worked when filling the buffer with 24 Bytes.
\begin{figure}[h]
  \centering
  \includegraphics[width=0.65\textwidth]{stackropoffsec.png}
  \caption{The stack when injecting the payload}
  \label{fig:mesh1}
\end{figure}
\subsection{ROP Chain}

@@

After specifying the goal and possibly simplifying it we have to write a list of instructions and arguments that achieve the goal, for this its favorable to directly use the format of the final payload except for using instructions instead of addresses as this will then allow to simply insert the found gadgets into this abstract payload. For the example in this paper we want to open a shell, for that the simplest way is to execute an execve system call. The following program state~\cref{fig:stateforint} has to be achieved so the interrupt \bltInlineVerb{int 0x80} causes a shell to be opened.

@@

  \includegraphics[width=0.95\textwidth]{Stateforexecve.png}
  \caption{Required program state for the execve syscall}

@@

\paragraph{Determining the padding}

@@

we have overwritten the return instruction pointer with \bltInlineVerb{"BBBB"}. Reducing the amount of \Verb+A+'s by 4 the first gadget overrides the return address of the function call and on \Verb+ret+ the execution gets redirected to the first gadget.

>>>>

\section{Theory}
\subsection{Stack}
The following graphic is an illustration of how the stack changes when injecting the payload. The buffer first has to be filled. In binary exploitation the letter \Verb+A+ is used for that most of the time, it has an easy to identify hexadecimal value of \bltInlineVerb{0x41}. It is important to note that without any special compiler options the stack will be aligned in \bltInlineVerb{dword}'s, because of that the buffer has to be filled with 16 Bytes instead of 8 Bytes, this can be turned off with the option \bltInlineVerb{-mpreferred-stack-boundary=2}. Though, then the payload only worked when filling the buffer with 24 Bytes.
\begin{figure}[h]
  \centering
  \includegraphics[width=0.79\textwidth]{stackropoffsec.png}
  \caption{The stack when injecting the payload}
  \label{fig:mesh1}
\end{figure}
\subsection{ROP Chain}

@@

After specifying the goal and possibly simplifying it we have to write a list of instructions and arguments that achieve the goal, for this its favorable to directly use the format of the final payload except for using instructions instead of addresses as this will then allow to simply insert the found gadgets into this abstract payload. For the example in this paper we want to open a shell, for that the simplest way is to execute an execve system call. The following program state~\cref{fig:stateforint} has to be achieved so the interrupt \bltInlineVerb{int 0x80} causes a shell to be opened.~\cite{pixis}

@@

  \includegraphics[width=0.95\textwidth]{requirementstackmemory.png}
  \caption{Required Program State for the execve Syscall}

@@

\paragraph{Determine the padding}

@@

\paragraph{Determine the address of a writable segment}
There segments in a binary can be read only or writable. It is possible to determine wether a segment is read only with \bltInlineVerb{objdump -h}. However, the following~\cref{command:finddatasegment} bash command can be used to find the address of the data segment.
\bltCommand{objdump.sh}{Determine the Address of .data}{command:finddatasegment}
